Paper Figs

### 2023-04-12 graphs_newt_snakes/Paper_figs.Rmd
I made some plot changes

@@

file$xmin = match(file$sim, target) - 0.5

file$xmax = match(file$sim, target) + 0.5

plot <-   ggplot(file_long) +
  ggtitle(title, subtitle = subt)+
  xlab(x_label) + ylab(y_label)+
geom_boxplot(aes(x=factor(sim, level=c("D", "C", "B", "H", "G", "L", "A", "F", "K", "P", "E", "J", "I", "O", "N", "M")), y=as.numeric(value), fill=factor(name)))+
  geom_rect(aes(xmin = as.numeric(xmin), xmax = as.numeric(xmax), ymin = -Inf, ymax = Inf, fill = rect_type)) +
  scale_fill_manual( values =c("darkred", "steelblue", "white","aliceblue" ), breaks = c('newt_pheno_change', 'snake_pheno_change', "True", "False"),  labels = c('Newt', 'Snake', "True", "False"))+ #labels=c("False",'Newt', 'Snake', "True")
      geom_boxplot(aes(x=factor(sim, level=c("D", "C", "B", "H", "G", "L", "A", "F", "K", "P", "E", "J", "I", "O", "N", "M")), y=as.numeric(value), fill=factor(name)),show.legend = FALSE)+
     theme(plot.title = element_text(size=5)) +
    labs(fill = " ")+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      title =element_text(size=8, face='bold'))

@@

@@

@@

title = "Phenotype Change Coevolution FLat Map"
boxplot_coevo_slope_flat_map(file3, title, subt, x_label, y_label)
```

>>>>

file$rect_type_a = ifelse(file$sim == "A" | file$sim == "B"| file$sim == "C" | file$sim == "D"| file$sim == "E"| file$sim == "I"| file$sim == "M", .9,1)

#target=c("D", "C", "B", "H", "G", "L", "A", "F", "K", "P", "E", "J", "I", "O", "N", "M")

#file$xmin = match(file$sim, target) - 0.5

#file$xmax = match(file$sim, target) + 0.5

plot <-   ggplot(file_long) +
  ggtitle(title, subtitle = subt)+
  xlab(x_label) + ylab(y_label)+
geom_boxplot(aes(x=factor(sim), y=as.numeric(value), fill=factor(name), alpha = rect_type_a))+ #, level=c("D", "C", "B", "H", "G", "L", "A", "F", "K", "P", "E", "J", "I", "O", "N", "M")
  #geom_rect(aes(xmin = as.numeric(xmin), xmax = as.numeric(xmax), ymin = -Inf, ymax = Inf, fill = rect_type)) +
  #scale_fill_manual( values =c("darkred", "steelblue", "white","aliceblue" ), breaks = c('newt_pheno_change', 'snake_pheno_change', "True", "False"),  labels = c('Newt', 'Snake', "True", "False"))+ #labels=c("False",'Newt', 'Snake', "True")
  scale_fill_manual( values = c("darkred", "steelblue" ), breaks = c('newt_pheno_change', 'snake_pheno_change'),  labels = c('Newt', 'Snake'))+
      #geom_boxplot(aes(x=factor(sim, level=c("D", "C", "B", "H", "G", "L", "A", "F", "K", "P", "E", "J", "I", "O", "N", "M")), y=as.numeric(value), fill=factor(name)),show.legend = FALSE)+
     theme(plot.title = element_text(size=5)) +
  scale_alpha(guide = 'none')+
    labs(fill = " ")+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      title =element_text(size=8, face='bold'))

boxplot_coevo_popsize_flat_map <- function(file, title, subt, x_label, y_label){

file$coevo_score[file$sim %in% newt_adv] = "Newt Advantage"
file$coevo_score[file$sim %in% mid] = "No Advantage"
file$coevo_score[file$sim %in% snake_adv] = "Snake Advantage"
file$rect_type = ifelse(file$sim == "A" | file$sim == "B"| file$sim == "C" | file$sim == "D"| file$sim == "E"| file$sim == "I"| file$sim == "M", "False","True")

file$rect_type_a = ifelse(file$sim == "A" | file$sim == "B"| file$sim == "C" | file$sim == "D"| file$sim == "E"| file$sim == "I"| file$sim == "M", .9,1)

@@

file_long <- tidyr::pivot_longer(file, c(Newt_pop_size, Snake_pop_size))

plot <-   ggplot(file_long[which(file_long$generation>=40000),]) +
  ggtitle(title, subtitle = subt)+
  xlab(x_label) + ylab(y_label)+
geom_boxplot(aes(x=factor(sim, level=c("D", "C", "B", "H", "G", "L", "A", "F", "K", "P", "E", "J", "I", "O", "N", "M")), y=as.numeric(value), fill=factor(name), alpha = rect_type_a))+
  scale_fill_manual( values = c("darkred", "steelblue" ), breaks = c('Newt_pop_size', 'Snake_pop_size'),  labels = c('Newt Pop Size', 'Snake Pop Size'))+
  theme(plot.title = element_text(size=5)) +
  scale_alpha(guide = 'none')+
  labs(fill = " ")+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      title =element_text(size=8, face='bold'))

@@

fast_slow_no_coevolution <- function(file, choices,min_gen, max_gen, title, subt, x_label, y_label){

   file<- subset(file, sim %in% choices)
   file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)

file$coevo_speed = 0

file$coevo_speed[file$sim %in% choices[1]] = "Fast Coevolution"
file$coevo_speed[file$sim %in% choices[2]] = "Slow Coevolution"
file$coevo_speed[file$sim %in% choices[3]] = "No Coevolution"
file$coevo_speed = factor(file$coevo_speed, levels=c("Fast Coevolution", "Slow Coevolution", "No Coevolution"))
plot <- ggplot(file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==0),]) +
    facet_wrap(~coevo_speed, ncol=1)+
    ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
    geom_line(aes(generation, Snake_mean_Pheno, color="Snake_mean_Pheno"),)+#group=rep
    geom_line(aes(generation, Newt_mean_Pheno, color="Newt_mean_Pheno"))+#group=rep
    #ylim(-1.,2.5)+
    xlab(x_label) + ylab(y_label)+
    scale_color_manual(name = "Species",
values = c( "Snake_mean_Pheno" = "steelblue", "Newt_mean_Pheno" = "darkred"),
labels = c("Snake", "Newt"))+
    theme_bw() + theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8),
                      title =element_text(size=8, face='bold'))
  return(plot)

@@

```{r, look at the change in phenotyp the plots}

@@

title = "Phenotype Change Coevolution FLat Map"
boxplot_coevo_slope_flat_map(file3, title, subt, x_label, y_label)

title = "Population Size Coevolution FLat Map"
y_label= "Population Size"
boxplot_coevo_popsize_flat_map(file3, title, subt, x_label, y_label)

file= GA1_lit
choices=c("K", "F", "E")
min_gen=100
max_gen=50000
title="Different Speeds of Coevolution" 
subt="" 
x_label= "Generations"
y_label= "Phenotype"
fast_slow_no_coevolution(file, choices, min_gen, max_gen, title, subt, x_label, y_label)
```
